\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Sabjel Pasha} \\ \vspace{6pt}
    \small 0874585049 $|$ \href{mailto:sabjel10@gmail.com}{\underline{sabjel10@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/sabjel-pasha?lipi=urn\%3Ali\%3Apage\%3Ad_flagship3_profile_view_base_contact_details\%3BFzu8iaabQKWTqNBau\%2BWMcw\%3D\%3D}{\underline{linkedin.com/in/sabjel-pasha}} $|$
    \href{https://github.com/Sabbbbb}{\underline{github.com/Sabbbbb}}
\end{center}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, C++, HTML/CSS, ARM Assembly, R, LaTeX, Processing} \\
     \textbf{Frameworks}{: JUnit, SDL/SDL2} \\
     \textbf{Developer Tools}{: Git, Visual Studio Code, Eclipse, Emacs, TMC Beans, R Studio, Processing} \\
    }}
 \end{itemize}

\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Trinity College Dublin}{Aug. 2021 -- Present}
      {Bachelor of Arts in Computer Science, Minor in Geography}{Dublin, Ireland}
      
\resumeProjectHeading
          {\textbf{Relevant Modules} $ $ \emph{}}{}
          \resumeItemListStart
            \resumeItem{Data Structures and Algorithms, Intro to Programming, Intermediate Programming, Intro to Computing, Programming Project, Statistical Analysis, Mathematics.}
          \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Space Object Project} $|$ \emph{Processing, Java, SmartSVN}}{Jan 2022 -- Mar. 2022}
          \resumeItemListStart
            \resumeItem{Developed an application to explore data relating to artificial space objects, such as satellites or debris.}
            \resumeItem{The data is read in from a public dataset from the General Catalog of Artificial Space Objects}
            \resumeItem{Sorted the objects from a .tsv file into arrays based on the mass, launch dates, current status, country etc.}
            \resumeItem{Implemented an interactive GUI which can be used to search for and neatly display space objects launched at the requested date, from a data set of 50,000 space objects}
            \resumeItem{Implemented a function which helps visualise the mass / altitude of the space objects by displaying objects within a specified altitude and drawing them on the screen relative to their real mass.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Sorting Algorithm Visualiser} $|$ \emph{C++, SDL/SDL2, Visual Studio Code}}{Sep. 2022 - Sep 2022}
          \resumeItemListStart
            \resumeItem{Developed a program that visualises an insertion sort algorithm in C++.}
            \resumeItem{Implemented SDL/SDL2 library to display the graphics via OpenGL.}
            \resumeItem{Creates an array with 100 randomly generated integers on each run.}
            \resumeItem{Each number in the array is represented as a vertical rectangle of relative height.}
            \resumeItem{Each step of the sorting algorithm is animated and the user can watch as the rectangles are sorted according to size and finally displayed in order.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IT Student Advisor}{Sep. 2022 -- Present}
      {IT Services, Trinity College Dublin}{Dublin, Ireland}
      \resumeItemListStart
        \resumeItem{Responsibility for College Network connection support for student owned PCs, laptops, and mobile devices.}
        \resumeItem{Providing general support and guidance on IT services to Trinity College students both on campus and at remote sites.}
        \resumeItem{Provision of advice and assistance with commonly used software applications at Trinity and for anti-virus and malware protection.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

 \section{Extracurricular Skills}
    \resumeItemListStart
            \resumeItem{Java Programming Course on \href{https://java-programming.mooc.fi/}{\underline{mooc.fi}}}
            \resumeItem{Fluent in English and Albanian}
            \resumeItem{Electric Guitar}
            \resumeItem{Building PCs}
    \resumeItemListEnd
\end{document}